Recpature distances

### 2024-04-02 recaptureanalysis/recaps.Rmd
working on diet data from cages and smelt recapgure data

recaps = read_excel("data/Running Delta Smelt Catch.xlsx", 
                    sheet = "Delta Smelt Catch Data") %>%
  rename( Latitude= `LatitudeStart`, Longitude = `LongitudeStart`) %>%
  mutate(FishID = paste("Fish", 1:nrow(recaps))) %>%
  select(-ReleaseDate, -Preservation, -Disposition, -SpecialStudyID, -MarkCode, -Dateknown)

@@

m2 = lm(Distance ~ Release, data = nndist)
summary(m2)
plot(m2)
#QQ plot is a bit of a mess I tried log-transforming and sqrt transforming and its still a mess.

emmeans(m2, pairwise ~ Release)
plot(emmeans(m2, pairwise ~ Release), comparisons = T)

@@

So DWSC soft were closer together than rio vista hard, but no difference between DWSC hard and DWSC soft

@@

```{r}
smeltIDS = select(recaps2, fishID, ReleaseEvent)

nndist2 = left_join(nndist, smeltIDS, by = c("Fish1" = "fishID"))

m3 = lm(Distance ~ ReleaseEvent, data = nndist2)
summary(m3)
plot(m3)
#QQ plot is a bit of a mess I tried log-transforming and sqrt transforming and its still a mess.

emmeans(m3, pairwise ~ ReleaseEvent)
plot(emmeans(m3, pairwise ~ ReleaseEvent), comparisons = T)

write.csv(nndist2, "DistanceMatrix.csv")
```

@@

smelt = read_excel("Data/smeltcatch_2023.xlsx")

smeltsf = st_as_sf(smelt, coords = c("LongitudeStart", "LatitudeStart"), crs = 4326) %>%
  mutate(Date = str_sub(as.character(SampleDate), 6, 10))

ggplot()+
  geom_sf(data = WW_Delta, fill = "grey90")+
  geom_sf(data = smeltsf, aes(shape = Survey, fill = LifeStage, color = LifeStage), size =5)+
  scale_shape_manual(values = c(23, 24, 25))+
  geom_sf_label(data = smeltsf, aes(label = Date), hjust =0, nudge_x = 0.01)+
  coord_sf(ylim = c(38.0, 38.45), xlim = c(-122.1, -121.55))+
  theme_bw()+
  ylab(NULL)+
  xlab(NULL)+
  annotation_scale()+
  annotation_north_arrow(aes(location = "tl"))

ggsave("Plots/smeltmap2023.tiff", device = "tiff", width =8, height =8)
ggsave("Plots/smeltmap2023.png", device = "png", width =8, height =8)

###########################################################
#map for Katie
smelt2 = read_excel("Data/Running Delta Smelt Catch_2023-09-05.xlsx", sheet = "Delta Smelt Catch Data")

smeltsf = st_as_sf(smelt2, coords = c("LongitudeStart", "LatitudeStart"), crs = 4326) %>%
  mutate(Date = str_sub(as.character(SampleDate), 6, 10)) %>%
  filter(SampleDate > ymd("2023-09-30"))

@@

ggsave("plots/Releasemap.png", device = "png", width =8, height =6)

>>>>

recaps = read_excel("data/Running Delta Smelt Catch.xlsx", 
                    sheet = "Delta Smelt Catch Data") %>%
  rename( Latitude= `LatitudeStart`, Longitude = `LongitudeStart`)

recaps = recaps %>%
  mutate(FishID = paste("Fish", 1:nrow(recaps))) %>%
  select(-ReleaseDate, -Preservation, -Disposition, -SpecialStudyID, -MarkCode, -Dateknown)

@@

m2 = lm(Distance ~ Type, data = alldist2)
summary(m2)
plot(m2)
#QQ plot is a bit of a mess I tried log-transforming and sqrt transforming and its still a mess.

emmeans(m2, pairwise ~ Type)
plot(emmeans(m2, pairwise ~ Type), comparisons = T)

@@

So soft were closer together than hard

@@

@@

###########################################################
#map for Katie
smelt2 = read_excel("data/Running Delta Smelt Catch.xlsx", 
                    sheet = "Delta Smelt Catch Data")

smeltsf = st_as_sf(smelt2, coords = c("LongitudeStart", "LatitudeStart"), crs = 4326) %>%
  mutate(Date = str_sub(as.character(SampleDate), 6, 10)) %>%
  filter(SampleDate > ymd("2023-09-30"), !is.na(ReleaseMethod))

@@

ggsave("plots/Releasemap.png", device = "png", width =8, height =6)
```
